### 2013-10-22 paper/paper.tex
Added figure in .tex file, added macros for (e.g, i.e)

\documentclass[11pt,twoside,a4paper]{article}
\usepackage{amssymb, amsmath}

@@

The complexity of a change can be very different from the complexity of the
files or system that contain a change (e.g., a change to many simple files
might be as complex as a change to one difficult file). Change complexity is
related to, ``how hard is it to understand and review a change" vs system
complexity, which measures for example, "how hard is it to understand and
potentially modify the system".

@@

\begin{enumerate}
\item[Source Line of Code] To define SLOC we use the definition given by Conte [Conte 1986]:
A line of code is any line of program text that is not a comment or blank line, regardless of the
number of statements or fragments of statements on the line. This specifically includes all lines containing program headers, declarations, and executable and non-executable statements.

\item[Lines of Code (LOC)]  Lines of code refers to the total number of lines in each source code file including comments and blank lines. It is a straightforward measure and can be calculated using many available tools.

\item[McCabe's Cyclomatic Complexity]
McCabe’s Cyclomatic complexity is one of the earliest complexity measures developed by Thomas J. McCabe in 1976. It directly measures the number of linearly independent paths through a program's source code. Any program can be represented as a graph with the simplest element being a flat series of statements with no conditions, loops or branches. [1] For a graph $G$ with $n$ vertices, $e$ edges and $p$ exit points, the complexity $v$ is defined as follows:

@@

\item  the churn or change size,

\item the number of modified files per commit,

\item the number of diffs per commit,

\item the number of and distance between contiguous change blocks within a diff
(\ie hunks),

\item the directory distance between files, and

\item depth of indentation of a change.

@@

{\bf Indentation:} Hindle \etal \cite{Hindle2008ICPC} created a complexity
measure that can be used to measure the complexity of the entire system or of a
change by examining the level of indentation on source lines. We calculate
their measure for reviews. They found that the strongest predictors of
complexity were the sum and standard deviation of the indentation of source
lines.

@@

TODO: this is where you put your figure and discription

>>>>

\documentclass[11pt,twoside,a4paper]{article}
\usepackage{amssymb, amsmath,graphicx,soul,color}

\newcommand*{\eg}{e.g. }
\newcommand*{\ie}{i.e. }

@@

The complexity of a change can be very different from the complexity of the
files or system that contain a change (\eg, a change to many simple files
might be as complex as a change to one difficult file). Change complexity is
related to, ``how hard is it to understand and review a change" vs system
complexity, which measures for example, "how hard is it to understand and
potentially modify the system".

@@

\begin{enumerate}
\item{\bf{Source Line of Code: }} To define SLOC we use the definition given by Conte [Conte 1986]:
A line of code is any line of program text that is not a comment or blank line, regardless of the
number of statements or fragments of statements on the line. This specifically includes all lines containing program headers, declarations, and executable and non-executable statements.

\item{\bf{Lines of Code (LOC): }} Lines of code refers to the total number of lines in each source code file including comments and blank lines. It is a straightforward measure and can be calculated using many available tools.

\item{\bf{McCabe's Cyclomatic Complexity: }}
McCabe’s Cyclomatic complexity is one of the earliest complexity measures developed by Thomas J. McCabe in 1976. It directly measures the number of linearly independent paths through a program's source code. Any program can be represented as a graph with the simplest element being a flat series of statements with no conditions, loops or branches. [1] For a graph $G$ with $n$ vertices, $e$ edges and $p$ exit points, the complexity $v$ is defined as follows:

@@

\item The churn or change size,

\item The number of modified files per commit,

\item The number of diffs per commit,

\item The number of and distance between contiguous change blocks within a diff
(\ie hunks),

\item The directory distance between files, and

\item The depth of indentation of a change.

@@

{\bf Indentation:} Hindle \cite{Hindle2008ICPC} created a complexity
measure that can be used to measure the complexity of the entire system or of a
change by examining the level of indentation on source lines. We calculate
their measure for reviews. They found that the strongest predictors of
complexity were the sum and standard deviation of the indentation of source
lines.

@@

\hl{TODO: this is where you put your figure and discription}

\begin{figure}[h!]
  \centering
   \includegraphics[width=1\textwidth]{change_complexity_figure}
   \caption{"Change Complexity vs. Traditional Complexity"}
\end{figure}
